The role of continuous developmental change in explaining discontinuities in word learning

### 2019-01-29 cogsci/cogsci.Rmd
second draft cogsci

In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and object pair on a 7-point scale. We processed the resulting data so that it can be used in the model. We normalized the values with respect to the most distant level, and we scaled them within the range [0,1]. Processed data are shown in Figure \ref{fig:stim}, for each stimuli group. This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).

>>>>

In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and object pair on a 7-point scale. We scaled responses within the range [0,1]. Data are shown in Figure \ref{fig:stim}, for each stimuli group. This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).

### 2019-01-29 cogsci/cogsci.tex
second draft cogsci

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and object pair
on a 7-point scale. We processed the resulting data so that it can be
used in the model. We normalized the values with respect to the most
distant level, and we scaled them within the range {[}0,1{]}. Processed
data are shown in Figure \ref{fig:stim}, for each stimuli group. This
data will be used in the models as the perceptual distance of sound
pairs (\(\Delta s\)) and object pairs (\(\Delta o\)).

>>>>

In a separate survey, \(N=20\) participants recruited on Amazon
Mechanical Turk evaluated the similarity of each sound and object pair
on a 7-point scale. We scaled responses within the range {[}0,1{]}. Data
are shown in Figure \ref{fig:stim}, for each stimuli group. This data
will be used in the models as the perceptual distance of sound pairs
(\(\Delta s\)) and object pairs (\(\Delta o\)).
